### 2019-12-10 CV/cv-sections/papers.tex
CV update

\cventry
{Adil Salim, Dmitry Kovalev, Peter Richtárik} % Role
{Stochastic Proximal Langevin Algorithm: Potential Splitting and Nonasymptotic Rates} % Title
{} % Location
{May 2019} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://arxiv.org/abs/1905.11768}{arXiv 2019}}
	\end{cvitems}
}

@@

\cventry
{Robert M. Gower, Dmitry Kovalev, Felix Lieder, Peter Richtárik} % Role
{RSN: Randomized Subspace Newton} % Title
{} % Location
{May 2019} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://arxiv.org/abs/1905.10874}{arXiv 2019}}
	\end{cvitems}
}

>>>>

\cventry
{Dmitry Kovalev, Konstantin Mishchenko, Peter Richtárik} % Role
{Stochastic Newton and Cubic Newton Methods with Simple Local Linear-Quadratic Rates} % Title
{} % Location
{Dec. 2019} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://drive.google.com/file/d/12aISV2e5XZGDxkr_wg9ILoC27HqoYJsV/view}{NeurIPS 2019 Workshop: Beyond First Order Methods in Machine Learning}}
	\end{cvitems}
}

\cventry
{Mohammad Alkousa, Darina Dvinskikh, Fedor Stonyakin, Alexander Gasnikov, Dmitry Kovalev} % Role
{Accelerated methods for composite non-bilinear saddle point problem} % Title
{} % Location
{Dec. 2019} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://arxiv.org/abs/1906.03620}{arXiv 2019}}
	\end{cvitems}
}

\cventry
{Adil Salim, Dmitry Kovalev, Peter Richtárik} % Role
{Stochastic Proximal Langevin Algorithm: Potential Splitting and Nonasymptotic Rates} % Title
{} % Location
{May 2019} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://papers.nips.cc/paper/8891-stochastic-proximal-langevin-algorithm-potential-splitting-and-nonasymptotic-rates}{NeurIPS 2019}}
	\end{cvitems}
}

@@

\cventry
{Robert M. Gower, Dmitry Kovalev, Felix Lieder, Peter Richtárik} % Role
{RSN: Randomized Subspace Newton} % Title
{} % Location
{May 2019} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://papers.nips.cc/paper/8351-rsn-randomized-subspace-newton}{NeurIPS 2019}}
	\end{cvitems}
}

### 2019-12-10 CV/cv-sections/talks.tex
CV update

\cventry
{Talk: <<Stochastic Spectral and Conjugate Descent Methods>>} % Role
{Weekly seminar <<Automatic control and Optimization Theory>>} % Event
{Institute for Control Problems, Moscow, Russia} % Location
{26 Mar. 2019} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{http://www.mathnet.ru/php/seminars.phtml?option_lang=rus&presentid=23658}{Link 1}}
		\item {\href{https://www.ipu.ru/node/50794}{Link 2}}
	\end{cvitems}
}

\cventry
{Talk: <<Stochastic Distributed Learning with Gradient Quantization and Variance Reduction>>}
{Seminar <<Modern Optimization Methods>>}
{Moscow Institute of Physics and Technology, Moscow, Russia}
{25 Mar. 2019}
{
	\begin{cvitems}
		\item {\href{https://vk.com/miptopt?w=wall-132864820_40\%2Fall}{Link}}
	\end{cvitems}
}

\cventry
{Poster Presenter: <<Stochastic Spectral Descent Methods>>} % Role
{Traditional School (Control, Information and Otimization)} % Event
{Voronovo, Moscow Region, Russia} % Location
{Jun. 2018} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://sites.google.com/site/traditionalschool/}{School website 1}}
		\item {\href{http://ssopt.org}{School website 2}}
	\end{cvitems}
}

\cventry
{Poster Presenter: Stochastic Spectral Descent Methods} % Role
{Optimization and Big Data Workshop} % Event
{KAUST, Thuwal, Saudi Arabia} % Location
{Feb. 2018} % Date(s)
{ % Description(s)
	\begin{cvitems}
		\item {\href{https://obd.kaust.edu.sa/}{Workshop website}}
		\item {\href{https://epostersonline.com/obd2018/node/51}{Poster}}
	\end{cvitems}
}

>>>>

\cventry
{Talk: <<Revisiting Stochastic Extragradient Method>>} % Role
{\href{https://iccopt2019.berlin/index.php}{ICCOPT 2019}} % Event
{TU, Berlin, Germany} % Location
{5 Aug. 2019} % Date(s)
{
}

\cventry
{\href{https://2019.ds3-datascience-polytechnique.fr/wp-content/uploads/2019/06/DS3-608_2019.pdf}{Poster: <<Stochastic Distributed Learning with Gradient Quantization and Variance Reduction>>}} % Role
{\href{https://2019.ds3-datascience-polytechnique.fr}{Data Science Summer School 2019}} % Event
{École polytechnique, Paris, France} % Location
{26 Jun. 2019} % Date(s)
{
}

\cventry
{Poster: <<Stochastic Distributed Learning with Gradient Quantization and Variance Reduction>>} % Role
{\href{http://ssopt.org}{Traditional School (Control, Information and Otimization)}} % Event
{Voronovo, Moscow Region, Russia} % Location
{20 Jun. 2019} % Date(s)
{
}

\cventry
{Talk: <<Stochastic Spectral and Conjugate Descent Methods>>} % Role
{\href{https://www.ipu.ru/node/50794}{Weekly seminar <<Automatic control and Optimization Theory>>}} % Event
{IPU, Moscow, Russia} % Location
{26 Mar. 2019} % Date(s)
{
}

\cventry
{Talk: <<Stochastic Distributed Learning with Gradient Quantization and Variance Reduction>>}
{\href{https://vk.com/miptopt?w=wall-132864820_40\%2Fall}{Seminar <<Modern Optimization Methods>>}}
{MIPT, Moscow, Russia}
{25 Mar. 2019}
{
}

\cventry
{Poster: <<Stochastic Spectral Descent Methods>>} % Role
{\href{https://sites.google.com/site/traditionalschool/}{Traditional School (Control, Information and Otimization)}} % Event
{Voronovo, Moscow Region, Russia} % Location
{Jun. 2018} % Date(s)
{
}

\cventry
{\href{https://epostersonline.com/obd2018/node/51}{Poster: Stochastic Spectral Descent Methods}} % Role
{\href{https://obd.kaust.edu.sa/}{Optimization and Big Data Workshop}} % Event
{KAUST, Thuwal, Saudi Arabia} % Location
{Feb. 2018} % Date(s)
{
}
